Contextual Combinatorial Cascading Bandits

### 2016-01-28 contextual combinatorial cascading bandits.tex

The main contributions of this paper can be summarized as follows: (1) we propose a general framework called contextual combinatorial cascading bandit that can many real-world application scenarios; 
(2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic 
	and real-world datasets and the results show that our algorithm effectively
	incorporates contextual information and position discounts with significant performance gains.

>>>>

The main contributions of this paper can be summarized as follows: (1) we propose a general framework  that incorporates contextual information,
position discounts, and general reward function to cover many real-world application scenarios; 
(2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic 
	and real-world datasets and the results show that our algorithm effectively
	incorporates contextual information and position discounts with significant performance gains.

\wei{The last two paragraphs have some repetition. 
	Is there any technical part in the algorithm and analysis that we would like to 
	mention in the introduction? So far the intro is only about conceptual additions to the model,
	and nothing about technical challenges and our solution. 
	It is ok if conceptual contribution is what we want to emphasize, but if there is any
	technical contribution we can say, we can also say it here.}
